---
title: "Skill Lab R_PS4"
author: "Bing-Jie Yen"
date: "February 16, 2017"
output: pdf_document
---
\section{Question 1}
 Use the code in the Session 4 script to reshape and table the tobacco retail
    policy scores by year, then plot the three barplots. Change the barplots to plot horizontally, using the horiz option, and change the number of columns and rows in the graphical parameters to recreate the plot below.





       
```{r}
score<-read.csv('F:/Dropbox/2017 Spring/Skill Lab  R/Data/stateRPAS_MPH5962.csv') #State retail tobacco policy scores


score2 <- reshape(score, varying=3:5, idvar="State", times=12:14, sep="",direction="long", drop="abbr")
score2$time <- score2$time +2000
head(score2)
library(ggplot2)
library(car)
score2$RPAS <- recode(score2$RPAS, recodes=
                        " 0:5='0-5';
                      6:10='6-10';
                      11:15='11-15';
                      16:20= '16-20';
                      21:25='21-25';
                      26:30='26-30';
                      31:33='31-33'
                      ", as.factor.result=T)


score2$time<-as.factor(score2$time)

ggplot(data=score2, aes(x=time, y=RPAS, fill=time)) +
  geom_bar(colour="black",stat="identity") +
  guides(fill=FALSE)+coord_flip()


       

```
\section{Question 1a}
1a. There are a few improvements from the plot above to the one below. Recreate the plot below. Remove the for loop and simply plot each of the three barplots individually.
```{r}

par(mfrow=c(1,3))
#2012
data2012 <- subset(score2, subset = time == 2012)
data2012$RPAS<-as.factor(data2012$RPAS)
plot(data2012$RPAS,horiz=TRUE,main="2012 Retail policy activity scores",col="green")

#2014
data2014 <- subset(score2, subset = time == 2014)
data2014$RPAS<-as.factor(data2014$RPAS)
plot(data2014$RPAS,horiz=TRUE,main="2014 Retail policy activity scores",col="blue")

#2015
data2015 <- subset(score2, subset = time == 2015)
data2015$RPAS<-as.factor(data2015$RPAS)
plot(data2015$RPAS,horiz=TRUE,main="2015 Retail policy activity scores",col="red")

```
\section{Question 2}
Use the plot function to create a scatterplot of the 2012 and 2015 tobacco retail
policy scores. Use the formula con???guration for plot (see help for plot.formula)
making the 2015 scores the "y" or dependent variable. Remember to change the
graphical parameters to accommodate only one plot. Change the x and y labels
from the variables to something more informative. Give the plot a title. Bonus:
change the points to solid circles or triangles, and change the color of the points.
```{r}
Q2<-ggplot(score, aes(score$RPAS12,score$RPAS15))

Q2+geom_point(shape=1) +    
  geom_smooth()   +
  xlab("2012 tobacco retail policy scores")+
  ylab("2015 tobacco retail policy scores")

```
\section{Question 3}
The boxplot command works just like the barplot command. Using the
County Health data, round the food environment index values to whole num- bers and create a boxplot of the distribution of the freeLunch variable for each
rounded value of the food environment index. Color the boxes and/or median
bars, label the axes and place an overall title. Since we often use the percent
of students eligible for free lunches as an indicator of economic prosperity of
```{r}
County <- read.csv('F:/Dropbox/2017 Spring/Skill Lab  R/Data/CountyHealth.csv')
County$roundedfei<-round(County$fei)
Q3<-ggplot(County, aes(factor(roundedfei), freeLunch))+  geom_boxplot(fill = "grey80", colour = "#3366FF")
Q3

```