---
title: "Skill Lab R - Problem 3"
author: "Bing-Jie Yen"
date: "February 9, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}
data.label<-read.csv('F:/Dropbox/2017 Spring/Skill Lab  R/Data/CountyHealthVariableLabels.csv')

data<-read.csv('F:/Dropbox/2017 Spring/Skill Lab  R/Data/CountyHealth.csv')
data<-data.frame(data)
names(data)
```
 1. Perform a t-test of difference-in-means on the rate of dentists per popula-
 tion in Virginia (FIPS=51) and Kentucky (FIPS=21). Is there a statistically
 significant difference in the averages?

 ANS: the t test (3.5198, p<0.001) shows that the difference in means is not equal to 0
 
```{r}
t.test(x=data[data$state== 51 ,11], y=data[data$state == 21,11])

```
2. From the full dataset, regress the rate of premature age-adjusted mortality
    on rates of adult diabetes, smoking, access to exercise, and limited healthy     food  options. Which predictors are statistically signifficant?

 ANS: all the predictors are statistically significant by simple linear regression with OLS method

```{r}
infMort<-data.frame(data$infMort)
diabAdult<-data.frame(data$diabAdult)
smokAdult<-data.frame(data$smokAdult)
accExer<-data.frame(data$accExer)
fei<-data.frame(data$fei)

Q2<-lm(infMort~diabAdult+smokAdult+accExer+fei,data=data)
summary(Q2)
```
3. Generate the predicted rates of premature age-adjusted mortality from your
    model. What is the average (mean) predicted value?
    calculate percent correctly predicted
 
```{r}
Q3<- data.frame(Q2$model$infMort, round(predict(Q2, type="response")))
names(Q3)<- c("obs", "pred")
#with(Q3, table(obs, pred))
summary(Q3)   
#with(Q3, table(obs, pred))/sum(table(Q3))
Q3accuracy<-100*sum(diag(with(Q3, table(obs, pred))/sum(table(Q3)))) 
```

4. Use the 'resid' function to generate the errors from your model. (HINT: The
  'resid' function works just like the 'predict' function.) Plot a histogram of the errors. Is the OLS assumption of a normal distribution of errors with a mean of zero met or is it violated?
  
```{r}
library(MASS)
Q4 <- studres(Q2) 
hist(Q4, freq=FALSE, 
     main="Distribution of Studentized Residuals")
xfit<-seq(min(Q4),max(Q4),length=40) 
yfit<-dnorm(xfit) 
lines(xfit, yfit)
```

5. Check the predictors in your model for multicollinearity. Which two predic-
  tors are most correlated, and what is the correlation coefficient?

ANS: with Variance inflation factor, diabAdult and smokAdult have highest variance inflation factors 
      
```{r}
library(car)
vif(Q2)  
cor(data$diabAdult,data$smokAdult,  use = "complete.obs")
```

6. Check the model for heteroskedasticity. Is the assumption of homoskedasticity
    met?
ANS: using Breush Pagan Test, the bptest shows that the model violates the assumption of homoskedasticity 

```{r}
library(lmtest)
bptest(Q2)
```
7. You are interested in which counties might have ine???cient health care sys-
  tems. You know that (price-adjusted) Medicare reimbursements paid per en-
  rollee are considered an indicator of a system's efficiency. You operationalize
  "inefficiency" in a county's health care system as a county's rate of these reimbursements being above the mean for counties. Create a binary variable of these reimbursements by county. Use this variable in the questions below.
  
```{r}
# Create the paMedReim mean 
paMedReim<-data.frame(data$paMedReim)
summary(paMedReim)   # Mean   : 9322  
data$inefficiency<-ifelse(paMedReim>9322,1,0)
inefficiency<-data.frame(data$inefficiency)
table(inefficiency) 
  
```

8. Execute a logistic regression model on the new variable. Include the      following regressors: primary care physicians per population, the food environment index, and smoking rates. Summarize the model.


```{r}
pcpRate<-data.frame(data$pcpRate)
Q8 <-glm(inefficiency ~ pcpRate+fei+smokAdult, family=binomial, data=data)
summary(Q8)
```

9. Find the odds ratios for the statistically signi???cant e???ects in the model (not the intercept).

 ANS: pcpRate and smokAdult are statistically significant and
 the odds ratio: pcpRate     0.99211743; smokAdult   1.19089448
 
 
```{r}
exp(cbind(OR = coef(Q8), confint(Q8)))

```

10. Calculate the percent of counties correctly predicted from your model.
 ANS: 65.45515  percent of counties are correctly predicted from the glm model Q8
 
 
```{r}
Q10<- data.frame(Q8$model$inefficiency, round(predict(Q8, type="response")))
names(Q10)<- c("obs", "pred")
with(Q10, table(obs, pred))

with(Q10, table(obs, pred))/sum(table(Q10))
Q10accuracy<-100*sum(diag(with(Q10, table(obs, pred))/sum(table(Q10))))
Q10accuracy 
```
